---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF - SS 2022/23"
author: "Yongyan Gao (12370014)"
date: "`r Sys.Date()`"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
library(tidyverse)
library(ggplot2)
library(lubridate)
library(knitr)
```

## General Remarks

-   You can submit your solutions in teams of up to 3 students.
-   Include all your team-member's names and student numbers
    (Martrikelnummern) in the `authors` field.
-   Please use the exercise template document to work on and submit your
    results.
-   Use a level 2 heading for each new exercise and answer each subtask
    next to it's bullet point or use a new level 3 heading if you want.
-   Always render the R code for your solutions and make sure to include
    the resulting data in your rendered document.
    -   Make sure to not print more than 10 rows of data (unless
        specifically instructed to).
-   Always submit both the rendered document(s) as well as your source
    Rmarkdown document. Submit the files separately on moodle, **not**
    as a zip archive.

## Exercise 1: Initializing git (4 Points)

For this whole exercise sheet we will be tracking all our changes to it
in git.

a)  Start by initializing a new R project with git support, called
    `exeRcise-sheet-3`. If you forgot how to do this, you can follow
    this
    [guide](https://malikaihle.github.io/Introduction-RStudio-Git-GitHub/rstudio_project.html).
b)  Commit the files generated by Rstudio.
c)  For all of the following tasks in this exercise sheet we ask you to
    always commit your changes after finishing each subtask e.g. create
    a commit after task *1d*, *1e* etc.

> Note: This applies only to answers that have text or code as their
> answer. If you complete tasks in a different order or forget to commit
> one, this is no problem. If you change your answers you can just
> create multiple commits to track the changes.

d)  Name 2 strengths and 2 weaknesses of git. (Don't forget to create a
    commit after this answer, see *1c*)  
    
Strengths: 1. Flexibility: offline work, faster operations, and the ability to         collaborate with others without a central server. 
           2. Branching and Merging: Creating branches allows users to work on multiple               features or bug fixes simultaneously without interfering with each other.  

Weaknesses: 1. Hard for Beginners: Understanding the Git workflow, branching strategies,                and resolving conflicts may require time and effort to master. 
            2. Command Line Complexity:  Executing complex Git operations solely may                   require memorizing specific commands and their options.



e)  Knit this exercise sheet. Some new files will automatically be
    generated when knitting the sheet e.g. the HTML page. Ignore these
    files, as we only want to track the source files themselves.

## Exercise 2: Putting your Repository on GitHub (3.5 Points)

For this task you will upload your solution to GitHub.

a)  Create a new repository on GitHub in your account named
    `exeRcise-sheet-3`. Make sure you create a **public repository** so
    we are able to see it for grading. Add the link to the repository
    below:
b)  Push your code to this new repository by copying and executing the
    snippet on github listed under
    `…or push an existing repository from the command line`.
c)  Regularly push your latest changes to GitHub again and especially do
    so when you are finished with this sheet.

## Exercise 3: Baby-Names in Munich (4.5 Points)

Download the latest open datasets on given names ("Vornamen") from the
open data repository of the city of Munich for the years `2022` and
`2021`.

Link: <https://opendata.muenchen.de/dataset/vornamen-von-neugeborenen>

a)  Download the data for both years and track it in git. For small
    datasets like these adding them to git is not a problem.


b)  Load the data for both years into R. Check the type of the count
    variable ("Anzahl") and look into the data to determine why it is
    not numeric? Fix the problem in an appropriate manner, it is OK if
    some of the counts are inaccurate because of this. Explain your
    solution and the repercussions.
    
```{r}

vorname_2021 <- read.csv("C:/Users/Yongyan/Documents/R/data/FortR23/vornamen_2021.csv")
vorname_2022 <- read.csv("C:/Users/Yongyan/Documents/R/data/FortR23/open_data_portal_2022.csv")

typeof(vorname_2021$Anzahl)
typeof(vorname_2022$Anzahl)

head(vorname_2021)
head(vorname_2022)

vorname_2021$Anzahl <- as.numeric(vorname_2021$Anzahl)
vorname_2022$Anzahl <- as.numeric(vorname_2022$Anzahl)

typeof(vorname_2021$Anzahl)
typeof(vorname_2022$Anzahl)

```
 
Fixing the problem with the "Anzahl" variable may result in some counts being inaccurate if there were non-numeric values or formatting issues in the original data. 

c)  Calculate the total number of babies born in Munich in 2022
    and 2021. Which year had the bigger baby-boom?
```{r}

vorname_2021 <- na.omit(vorname_2021)
vorname_2022 <- na.omit(vorname_2022)

total_2021 <- sum(vorname_2021$Anzahl)
total_2022 <- sum(vorname_2022$Anzahl)

total_2021
total_2022

```
2021 had the bigger baby-boom. 

d)  Add a new column `year` to both datasets which holds the correct
    year for each.
```{r}
library(dplyr)

vorname_2021 <- mutate(vorname_2021, year = 2021)
vorname_2022 <- mutate(vorname_2022, year = 2022)

head(vorname_2021)
head(vorname_2022)
```

e)  Combine both datasets into one using `bind_rows()`.

```{r}
combined_data <- bind_rows(vorname_2021, vorname_2022)
head(combined_data)
```


f)  Combine the counts for same names to determine the most popular
    names across both years. Print out the top 10 names in a nicely
    formatted table for both years. Include a table caption.
    
```{r}
popular_names <- combined_data %>%
  group_by(ï..Vorname) %>%
  summarize(Total_Count = sum(Anzahl))

top_10_names <- popular_names %>%
  arrange(desc(Total_Count)) %>%
  head(10)

caption <- "Top 10 Popular Names in Munich (2021-2022)"
kable(top_10_names, caption = caption, align = "c", format = "markdown")
```

## Exercise 4: Chat GPT + apply (3 points)

For this task: Specifically use ChatGPT to solve the task and submit
your prompts in addition to the solution

a)  The code below does not work because the wrong apply function has
    been used. Find out which apply function would be correct and why it
    did not work. Correct the code. Also calculate the rowwise means.

###Create a sample data frame

tax_data \<- data.frame( Name = c("Munich GmbH", "ABC Inc.", "Backpacks
1980", "Bavarian Circus"), Tax_2019 = c(5000, 4000, 6000, 3500),
Tax_2020 = c(4800, 4200, 5800, 3700), Tax_2021 = c(5200, 3800, 5900,
3400) )

###Calculate column-wise means

column_means \<- lapply(tax_data\[, -1\], 2, mean)

column_means

```{r}
tax_data <- data.frame(
  Name = c("Munich GmbH", "ABC Inc.", "Backpacks 1980", "Bavarian Circus"),
  Tax_2019 = c(5000, 4000, 6000, 3500),
  Tax_2020 = c(4800, 4200, 5800, 3700),
  Tax_2021 = c(5200, 3800, 5900, 3400)
)

# Calculate column-wise means
column_means <- sapply(tax_data[, -1], mean)

column_means

# Calculate row-wise means
row_means <- rowMeans(tax_data[, -1])

row_means
```

b)  Using ChatGPT try to understand what the rapply() function does.
    Create an easy example with mock data where the function is used and
    explain it in your words. 
    
The rapply() function in R is used to recursively apply a function to elements of a list or nested list structure. It traverses through the given list and applies a specified function to each element, including elements within nested lists. 

```{r}
# Create a nested list structure
data <- list(
  a = 1,
  b = list(
    c = 2,
    d = list(
      e = 3,
      f = 4
    )
  )
)

# Define a function to add 10 to numeric values
add_10 <- function(x) {
  if (is.numeric(x)) {
    x + 10
  } else {
    x
  }
}

# Apply the add_10 function recursively using rapply
modified_data <- rapply(data, add_10)

modified_data
```
In this example, we have a nested list structure called data. It contains numeric values (1, 2, 3, 4) at different levels within the structure. We want to add 10 to all the numeric values in the structure while keeping the non-numeric values unchanged.

We define the add_10 function, which checks if the input x is numeric. If it is, the function adds 10 to it; otherwise, it returns x as it is.

We then apply the add_10 function recursively to the data structure using rapply(). The function traverses through the list structure and applies the add_10 function to each numeric value it encounters. The resulting modified list structure, modified_data, is returned with the numeric values incremented by 10.

In the example, modified_data will be a nested list with the same structure as data, but with all the numeric values increased by 10.

## Final Note

Make sure to push all your commits and changes to GitHub before
submittining the exercise sheet.
